---
title: "Models"
output: html_notebook
---

### Load libraries

```{r}
library(plm)
library(lmtest)
library(dplyr)
library(crosstable)
```

### Fixed effects

```{r}
data <- read.csv("final_w456.csv")
#data <- read.csv("data_clean_w46.csv")
```

```{r}
# age squared
data$age_squared <- data$age^2
```

# work_horizon_change continuous

```{r}
fe_mod <- plm(eurod ~ work_horizon + work_horizon_change + age + I(age_squared) + partnerinhh + nb_children + gender + yrseducation, #+ jqi_monthly_earnings + jqi_skills_discretion + jqi_social_environment + jqi_physical_environment + jqi_intensity + jqi_prospects + jqi_working_time_quality + factor(country) + factor(isco),
               data = data,
               index = c("mergeid", "year"),
               model = "within")
coeftest(fe_mod, vcov. = vcovHC, type = "HC1")
```

# work_horizon_change binary (1 if >1)

```{r}
data$work_horizon_change_bin <- ifelse(data$work_horizon_change > 1, 1, 0)

fe_mod <- plm(eurod ~ work_horizon + work_horizon_change_bin + age + I(age_squared) + partnerinhh + nb_children + gender + yrseducation, #+ jqi_monthly_earnings + jqi_skills_discretion + jqi_social_environment + jqi_physical_environment + jqi_intensity + jqi_prospects + jqi_working_time_quality + factor(isco) + factor(country),
               data = data,
               index = c("mergeid", "year"),
               model = "within")
coeftest(fe_mod, vcov. = vcovHC, type = "HC1")
```

# work_horizon_change categoric

```{r}
data$work_horizon_change_cat <- cut(data$work_horizon_change, breaks = c(-Inf, 0, 1, 2, Inf), labels = c("0", "<1", "<2", "2+"), include.lowest = TRUE)


fe_mod <- plm(eurod ~ work_horizon + work_horizon_change_cat + age + I(age_squared) + partnerinhh + nb_children + gender + yrseducation + jqi_monthly_earnings + jqi_skills_discretion + jqi_social_environment + jqi_physical_environment + jqi_intensity + jqi_prospects + jqi_working_time_quality + factor(country) + factor(isco),
               data = data,
               index = c("mergeid", "year"),
               model = "within")
coeftest(fe_mod, vcov. = vcovHC, type = "HC1")
```



### DID
Load data
```{r}
data <- read.csv("/Users/alexandralugova/Documents/GitHub/MH-old-workers/data/datasets/results/4digits_w46_year_balanced.csv")
```

Create some additional variables
```{r}
# Explanatory variables
# age squared
data$age_squared <- data$age^2
# income log
data$thinc_log <- log(data$thinc + 1)
data$thinc2_log <- log(data$thinc2 + 1)
# work horizon change binary
data$work_horizon_change_bin0 <- ifelse(data$work_horizon_change > 0, 1, 0)
data$work_horizon_change_bin1 <- ifelse(data$work_horizon_change > 1, 1, 0)
# work horizon change categorical
data$work_horizon_change_cat <- cut(data$work_horizon_change, breaks = c(-Inf, 0, 1, 2, Inf), labels = c("0", "<1", "<2", "2+"), include.lowest = TRUE)

# DID variables
# post treatment period
data$time = ifelse(data$year >= 2015, 1, 0)
# treatment group if work_horizon_change > 0
mergeids_to_treat <- data %>%
  filter(time == 1 & work_horizon_change > 0) %>%
  select(mergeid) %>%
  distinct()
data <- data %>%
  mutate(treated = ifelse(mergeid %in% mergeids_to_treat$mergeid, 1, 0))
# did
data$did = data$time * data$treated
```

Descriptive statistics
```{r}
# demographics
data_summary <- data %>% dplyr::select(gender, age, nb_children, nb_grandchildren, partnerinhh, yrseducation, thinc, investment, life_insurance)
knitr::kable(psych::describe(data_summary, skew = FALSE), digits = c(1,4,2,2,1,1,1,3))
```

```{r}
# work
data_summary <- data %>% dplyr::select(yrscontribution, retirement_age, work_horizon, work_horizon_change, jqi_skills_discretion, jqi_physical_environment, jqi_social_environment, jqi_working_time_quality, jqi_prospects, jqi_intensity, jqi_sum)
knitr::kable(psych::describe(data_summary, skew = FALSE), digits = c(1,4,2,2,1,1,1,3))
```

```{r}
# health
data_summary <- data %>% dplyr::select(sphus, sphus2, chronic, chronic2, eurod, eurodcat, affective_suffering, motivation_lack)
knitr::kable(psych::describe(data_summary, skew = FALSE), digits = c(1,4,2,2,1,1,1,3))
```

Cross table and different tests
```{r}
# demographics
crosstable(data, c(gender, age, nb_children, nb_grandchildren, partnerinhh, yrseducation, thinc, investment, life_insurance), by=eurodcat, test=TRUE) %>%
  as_flextable(fontsizes = list(body = 8, subheaders = 8, header = 8),)
```

```{r}
# work
crosstable(data, c(yrscontribution, retirement_age, work_horizon, work_horizon_change, work_horizon_change_bin0, work_horizon_change_bin1, work_horizon_change_cat, job_status, industry, jqi_skills_discretion, jqi_physical_environment, jqi_social_environment, jqi_working_time_quality, jqi_prospects, jqi_intensity, jqi_sum), by=eurodcat, test=TRUE) %>%
  as_flextable(fontsizes = list(body = 8, subheaders = 8, header = 8),)
```

```{r}
# health
crosstable(data, c(sphus, sphus2, chronic, chronic2), by=eurodcat, test=TRUE) %>%
  as_flextable(fontsizes = list(body = 8, subheaders = 8, header = 8),)
```

# Basic DID

```{r}
didreg = lm(eurod ~ treated + time + did, data = data)
summary(didreg)
```

# DID with explanatory variables
```{r}
didreg = lm(eurod ~ treated + time + did + age + I(age_squared) + gender + nb_children + nb_grandchildren + partnerinhh + yrseducation + thinc + thinc_log + investment + life_insurance + sphus + chronic + work_horizon + jqi_skills_discretion + jqi_physical_environment + jqi_social_environment + jqi_working_time_quality + jqi_prospects + jqi_intensity + factor(industry) + factor(country), data = data)
summary(didreg)
```

# DID with explanatory variables EuroD binary
```{r}
logit_reg <- glm(eurodcat ~ treated + time + did + age + I(age_squared) + gender + nb_children + nb_grandchildren + partnerinhh + yrseducation + thinc + thinc_log + investment + life_insurance + sphus + chronic + work_horizon + jqi_skills_discretion + jqi_physical_environment + jqi_social_environment + jqi_working_time_quality + jqi_prospects + jqi_intensity + factor(industry) + factor(country), data = data,
                 family = binomial(link = "logit"))
summary(logit_reg)
```

# DID with fixed effects
```{r}
pdata <- pdata.frame(data, index = c("mergeid", "year"))
```

```{r}
didreg <- plm(eurod ~ treated + time + did + age + I(age_squared) + gender + nb_children + nb_grandchildren + partnerinhh + yrseducation + thinc + thinc_log + investment + life_insurance + sphus + chronic + work_horizon + jqi_skills_discretion + jqi_physical_environment + jqi_social_environment + jqi_working_time_quality + jqi_prospects + jqi_intensity,
              data = pdata, model = "within", effect = "individual")

# Display summary
summary(didreg)
```





# DID for physcial environment above mean

```{r}
mean_physical_environment <- mean(data$jqi_physical_environment)
filtered_data <- data[data$jqi_physical_environment > mean_physical_environment, ]

didreg = lm(eurod ~ treated + time + did + age + I(age_squared) + gender + nb_children + partnerinhh + yrseducation + work_horizon + jqi_monthly_earnings + jqi_skills_discretion + jqi_social_environment + jqi_intensity + jqi_prospects + jqi_working_time_quality, data = filtered_data)
summary(didreg)
```
