---
title: "Models"
output: html_notebook
---

### Load libraries

```{r}
library(plm)
library(lmtest)
library(dplyr)
library(crosstable)
library(did)
library(car)
library(corrplot)
library(ggplot2)
library(glmnet)
library(MASS)
```

### Load data
```{r}
data <- read.csv("/Users/alexandralugova/Documents/GitHub/MH-old-workers/data/datasets/results/4digits_w46_year_balanced.csv")
```

### Create some additional variables
```{r}
# Explanatory variables
# age squared
data$age_squared <- data$age^2
# income log
data$thinc_log <- log(data$thinc + 1)
data$thinc2_log <- log(data$thinc2 + 1)
# children and grandchildren together

# work horizon change binary
data$work_horizon_change_bin0 <- ifelse(data$work_horizon_change_total > 0, 1, 0)
data$work_horizon_change_bin1 <- ifelse(data$work_horizon_change_total > 1, 1, 0)
# work horizon change categorical
data$work_horizon_change_cat <- cut(data$work_horizon_change_total, breaks = c(-Inf, 0, 1, 2, Inf), labels = c("0", "<1", "<2", "2+"), include.lowest = TRUE)

# DID variables
# post treatment period
data$time = ifelse(data$year >= 2015, 1, 0)
# treatment group if work_horizon_change > 0
mergeids_to_treat <- data %>%
  filter(time == 1 & work_horizon_change_total > 0) %>%
  distinct(mergeid)
data <- data %>%
  mutate(treated = ifelse(mergeid %in% mergeids_to_treat$mergeid, 1, 0))
# did
data$did = data$time * data$treated

# Determine cell fol fixed effects/ cluster standard errors
data$cell <- paste(data$country, data$gender, sep = "_")

# Interactions of indexes
interaction_terms <- model.matrix(~ (jqi_skills_discretion + jqi_physical_environment +
  jqi_social_environment + jqi_working_time_quality +
  jqi_prospects + jqi_intensity)^2, data = data)

interaction_terms <- interaction_terms[, -c(1, 2, 3, 4, 5, 6, 7)]
interaction_terms_colnames <- colnames(interaction_terms)

data <- cbind(data, interaction_terms)

# For YTR between 0 and 1 only
#sum_by_mergeid <- data %>% group_by(mergeid) %>% summarize(total_work_horizon_change = sum(work_horizon_change, na.rm = TRUE))
#mergeid_to_remove <- sum_by_mergeid %>% filter(total_work_horizon_change > 1) %>% pull(mergeid)
#data <- data %>% filter(!(mergeid %in% mergeid_to_remove))
```

Number of treated individuals
```{r}
sum(data$did)
```

### Descriptive statistics

```{r}
# correlations
cor_matrix <- cor(data[, c("age","gender","nb_children","nb_grandchildren","partnerinhh","yrseducation","thinc","investment","life_insurance","sphus","chronic",
                           "eurod","work_horizon", "work_horizon_change", "jqi_skills_discretion_pure", "jqi_physical_environment_pure",
                           "jqi_social_environment_pure","jqi_working_time_quality_pure", "jqi_prospects_pure", "jqi_intensity_pure")])

corrplot(cor_matrix, method = "color", col = colorRampPalette(c("lightgreen", "white", "salmon"))(20),tl.cex = 0.7)
```
```{r}
# correlations
cor_matrix <- cor(data[, c("jqi_skills_discretion_pure", "jqi_physical_environment_pure",
                           "jqi_social_environment_pure","jqi_working_time_quality_pure", "jqi_prospects_pure", "jqi_intensity_pure")])

corrplot(cor_matrix, method = "number", col = colorRampPalette(c("lightgreen", "white", "salmon"))(20),tl.cex = 0.7)
```


```{r}
# demographics
data_summary <- data %>% dplyr::select(gender, age, nb_children, nb_grandchildren, partnerinhh, yrseducation, thinc, investment, life_insurance)
knitr::kable(psych::describe(data_summary, skew = FALSE), digits = c(1,4,2,2,1,1,1,3))
```

```{r}
# work
data_summary <- data %>% dplyr::select(yrscontribution, retirement_age, work_horizon, work_horizon_change, jqi_skills_discretion_pure, jqi_physical_environment_pure, jqi_social_environment_pure, jqi_working_time_quality_pure, jqi_prospects_pure, jqi_intensity_pure, jqi_sum_pure)
knitr::kable(psych::describe(data_summary, skew = FALSE), digits = c(1,4,2,2,1,1,1,3))
```

```{r}
# health
data_summary <- data %>% dplyr::select(sphus, sphus2, chronic, chronic2, eurod, eurodcat, affective_suffering, motivation_lack)
knitr::kable(psych::describe(data_summary, skew = FALSE), digits = c(1,4,2,2,1,1,1,3))
```

### Cross table and different tests
```{r}
crosstable(subset(data, time == 0), c(eurod, eurodcat), by=treated, test=TRUE) %>%
  as_flextable(fontsizes = list(body = 8, subheaders = 8, header = 8),)
```


```{r}
# demographics
crosstable(data, c(gender, age, nb_children, nb_grandchildren, partnerinhh, yrseducation, thinc, investment, life_insurance), by=eurodcat, test=TRUE) %>%
  as_flextable(fontsizes = list(body = 8, subheaders = 8, header = 8),)
```

```{r}
# work
crosstable(data, c(yrscontribution, retirement_age, work_horizon, work_horizon_change, work_horizon_change_bin0, work_horizon_change_bin1, work_horizon_change_cat, job_status), by=eurodcat, test=TRUE) %>%
  as_flextable(fontsizes = list(body = 8, subheaders = 8, header = 8),)
```


```{r}
# work quality
crosstable(data, c(jqi_skills_discretion_pure, jqi_physical_environment_pure, jqi_social_environment_pure, jqi_working_time_quality_pure, jqi_prospects_pure, jqi_intensity_pure, jqi_sum_pure), by=eurodcat, test=TRUE) %>%
  as_flextable(fontsizes = list(body = 8, subheaders = 8, header = 8),)
```


```{r}
# health
crosstable(data, c(sphus, sphus2, chronic, chronic2), by=eurodcat, test=TRUE) %>%
  as_flextable(fontsizes = list(body = 8, subheaders = 8, header = 8),)
```

# DID models
```{r}
interaction_formula <- paste(interaction_terms_colnames, collapse = " + ")
full_formula <- reformulate(c("time", "treated", "did", "age", "I(age^2)", "nb_children",
                              "nb_grandchildren", "partnerinhh",  "yrseducation", "thinc2",
                              "thinc2_log", "investment", "life_insurance", "sphus", "chronic",
                              "work_horizon", "jqi_skills_discretion",
                              "jqi_physical_environment", "jqi_social_environment",
                              "jqi_working_time_quality", "jqi_prospects",
                              "jqi_intensity", interaction_formula, "factor(cell)",
                              "factor(industry)"), response = "eurod")
noint_formula <- reformulate(c("treated", "did", "age", "I(age^2)", "nb_children",
                              "nb_grandchildren", "partnerinhh", "yrseducation", "thinc2",
                              "thinc2_log", "investment", "life_insurance", "sphus", "chronic",
                              "work_horizon", "jqi_skills_discretion",
                              "jqi_physical_environment", "jqi_social_environment",
                              "jqi_working_time_quality", "jqi_prospects",
                              "jqi_intensity", "factor(cell)",
                              "factor(industry)"), response = "eurod")
noind_formula <- reformulate(c("time", "treated", "did", "age", "I(age^2)", "nb_children",
                              "nb_grandchildren", "partnerinhh", "yrseducation", "thinc2",
                              "thinc2_log", "investment", "life_insurance", "sphus", "chronic",
                              "work_horizon", "jqi_sum", "factor(cell)",
                              "factor(industry)"), response = "eurod")
```



```{r}
data$eurodlog <- log(data$eurod + 1e-8)
did_full <- lm(eurodlog ~ time + treated + did + age + I(age^2) + nb_children +
                              nb_grandchildren + partnerinhh + yrseducation + thinc2 +
                              thinc2_log + investment + life_insurance + sphus + chronic +
                              work_horizon + jqi_skills_discretion +
                              jqi_physical_environment + jqi_social_environment +
                              jqi_working_time_quality + jqi_prospects +
                              jqi_intensity + factor(cell) + factor(industry), data = data, weights = my_wgt)
#did_full <- glm(noint_formula, data = data, weights = my_wgt,family = poisson)
#did_full <- glm(noint_formula, data = data, weights = my_wgt,family = binomial)
summary(did_full)
```


```{r}
# DID full dataset
did_full <- lm(full_formula, data = data, weights = my_wgt)
# DID full dataset panel fixed effects
did_full_plm = plm(full_formula, data = data, weights = my_wgt, index = c("mergeid","year"), model = "within")

# DID female/male
did_female = plm(full_formula, data = subset(data, gender == 1), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_male = plm(full_formula, data = subset(data, gender == 0), weights = my_wgt, index = c("mergeid","year"), model = "within")

# DID female/male jqi_skills_discretion above/below mean
did_female_skills_high = plm(full_formula, data = subset(data, gender == 1 & jqi_skills_discretion >= mean(jqi_skills_discretion)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_female_skills_low= plm(full_formula, data = subset(data, gender == 1 & jqi_skills_discretion < mean(jqi_skills_discretion)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_male_skills_high = plm(full_formula, data = subset(data, gender == 0 & jqi_skills_discretion >= mean(jqi_skills_discretion)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_male_skills_low = plm(full_formula, data = subset(data, gender == 0 & jqi_skills_discretion < mean(jqi_skills_discretion)), weights = my_wgt, index = c("mergeid","year"), model = "within")

# DID female/male jqi_physical_environment above/below mean
did_female_physical_high = plm(full_formula, data = subset(data, gender == 1 & jqi_physical_environment >= mean(jqi_physical_environment)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_female_physical_low = plm(full_formula, data = subset(data, gender == 1 & jqi_physical_environment < mean(jqi_physical_environment)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_male_physical_high = plm(full_formula, data = subset(data, gender == 0 & jqi_physical_environment >= mean(jqi_physical_environment)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_male_physical_low = plm(full_formula, data = subset(data, gender == 0 & jqi_physical_environment < mean(jqi_physical_environment)), weights = my_wgt, index = c("mergeid","year"), model = "within")

# DID female/male jqi_social_environment above/below mean
did_female_social_high = plm(full_formula, data = subset(data, gender == 1 & jqi_social_environment >= mean(jqi_social_environment)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_female_social_low = plm(full_formula, data = subset(data, gender == 1 & jqi_social_environment < mean(jqi_social_environment)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_male_social_high = plm(full_formula, data = subset(data, gender == 0 & jqi_social_environment >= mean(jqi_social_environment)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_male_social_low = plm(full_formula, data = subset(data, gender == 0 & jqi_social_environment < mean(jqi_social_environment)), weights = my_wgt, index = c("mergeid","year"), model = "within")

# DID female/male jqi_working_time_quality above/below mean
did_female_time_high = plm(full_formula, data = subset(data, gender == 1 & jqi_working_time_quality >= mean(jqi_working_time_quality)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_female_time_low = plm(full_formula, data = subset(data, gender == 1 & jqi_working_time_quality < mean(jqi_working_time_quality)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_male_time_high = plm(full_formula, data = subset(data, gender == 0 & jqi_working_time_quality >= mean(jqi_working_time_quality)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_male_time_low = plm(full_formula, data = subset(data, gender == 0 & jqi_working_time_quality < mean(jqi_working_time_quality)), weights = my_wgt, index = c("mergeid","year"), model = "within")

# DID female/male jqi_prospects above/below mean
did_female_prospects_high = plm(full_formula, data = subset(data, gender == 1 & jqi_prospects >= mean(jqi_prospects)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_female_prospects_low = plm(full_formula, data = subset(data, gender == 1 & jqi_prospects < mean(jqi_prospects)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_male_prospects_high = plm(full_formula, data = subset(data, gender == 0 & jqi_prospects >= mean(jqi_prospects)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_male_prospects_low = plm(full_formula, data = subset(data, gender == 0 & jqi_prospects < mean(jqi_prospects)), weights = my_wgt, index = c("mergeid","year"), model = "within")

# DID female/male jqi_intensity above/below mean
did_female_intensity_high = plm(full_formula, data = subset(data, gender == 1 & jqi_intensity >= mean(jqi_intensity)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_female_intensity_low = plm(full_formula, data = subset(data, gender == 1 & jqi_intensity < mean(jqi_intensity)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_male_intensity_high = plm(full_formula, data = subset(data, gender == 0 & jqi_intensity >= mean(jqi_intensity)), weights = my_wgt, index = c("mergeid","year"), model = "within")
did_male_intensity_low = plm(full_formula, data = subset(data, gender == 0 & jqi_intensity < mean(jqi_intensity)), weights = my_wgt, index = c("mergeid","year"), model = "within")
```

```{r}
summary(did_full_plm)
```


```{r}
summary(did_female)
```

```{r}
summary(did_female_intensity_low)
```


Clusterization of standard errors
```{r}
clustered_se <- vcovHC(did_female, type = "HC1", cluster = "cell") # Cluster standard errors at the country level
robust_se <- sqrt(diag(clustered_se)) # Obtain robust standard errors

coeftest(did_female, vcov. = clustered_se)
```

# Tests
```{r}
par(mfrow = c(2, 2))
plot(did_full)
```

Normality of residuals - DID approach is robust to this

Breusch-Pagan test for heteroscedasticity
```{r}
bptest(did_full) #small p-value - not normal - heteroscedasticity present
```

```{r}
# Multicollinearity VIF TEST
vif(did_full)
```

Ensure that the treatment and control groups are comparable
```{r}
# crosstable
```

Parallel trends test
```{r}
# load previous waves and inspect eurod for treated and not treated individuals
```

`
